Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-10-21 juan/draft/draft.tex
progress

Consider a set of $N=n+1$ teams labeled $\{0,1,\dots,n\}$.
For each distinct pair of teams $i$ and $j$, assume a pairwise comparison score $f_{ij}=-f_{ji}$ is available.
Informally, $f_{ij}>0$ indicates that team $i$ is rated higher than team $j$, whereas $f_{ij}<0$ suggests the opposite.

@@

For each pair $\{i,j\}$ of teams in a given league, several pairwise metrics $m_{ij}$ and $m_{ji}$ are recorded.
Each metric $m_{ij}$ takes a positive value when it favors team $i$ over $j$, and a negative value otherwise.
The metrics considered include:
\begin{enumerate}
\item \textbf{crossings}
\item \textbf{counterattacks}
\item \textbf{pressure loss}
\item \textbf{build-up time}
\item \textbf{direct play}
\item \textbf{pressure points}
\item \textbf{shots}
\item \textbf{flow rate}
\item \textbf{maintenance time}
\item \textbf{middle-zone time} (etc.)
\end{enumerate}
Additionally, the Singular Value Decomposition of these empirical metrics is considered to define higher-level descriptors called \emph{styles}~\cite{chacoma2025data}.

>>>>

Consider a set of $N=n+1$ teams labeled $\{0,1,\dots,n\}$.
For each distinct pair of teams $i$ and $j$, assume a pairwise antisymmetric comparison score $f_{ij}=-f_{ji}$ is available.
Informally, $f_{ij}>0$ indicates that team $i$ is rated higher than team $j$, whereas $f_{ij}<0$ suggests the opposite.

@@

For each pair $\{i,j\}$ of teams in a given league, several pairwise antisymmetric comparison scores $f_{ij}$ are defined:
\begin{enumerate}
\item \textbf{crossings:} ...
\item \textbf{counterattacks:} ...
\item \textbf{pressure loss:} ...
\item \textbf{build-up time:} ...
\item \textbf{direct play:} ...
\item \textbf{pressure points:} ...
\item \textbf{shots:} ...
\item \textbf{flow rate:} ...
\item \textbf{maintenance time:} ...
\item \textbf{middle-zone time:} ...
\item \textbf{style:} the Singular Value Decomposition (SVD) of previous metrics is used to define higher-level descriptors called \emph{styles}, so $f_{ij}=...$~\cite{chacoma2025data}.
\item \textbf{rank based ground-truth:} $f_{ij}=i-j$.
\item \textbf{point based ground-truth:} $f_{ij}=\pi_j-\pi_i$.
\end{enumerate}
